Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2024-02-12 output/paper/_figures.qmd
Trying to fix Table 1, now with by cohort only in SM. Modifying names EDCs in forest plots.

```{r}
# Function to align forest plot with table numerical results
forest_plot <- function(obj, r = 4) {
  # From table of numerical results to ggplot object
  tbl_num_res <- obj$numerical_results |>
    tidylog::mutate(
      variable = forcats::fct_reorder2(
        variable, estimate, class
      )
    ) |>
    tidylog::select(-estimate) |>
    ggplot2::ggplot(
      ggplot2::aes(
        y = variable,
        shape = outcome
      )
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 0,
        label = variable
      ),
      hjust = 0,
      fontface = "bold"
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 1,
        label = val
      ),
      hjust = 0,
      position = ggstance::position_dodgev(height = 0.9)
    ) +
    ggplot2::theme_void() +
    ggplot2::theme(
      strip.background = ggplot2::element_blank(),
      strip.text = ggplot2::element_blank(),
      legend.position = "bottom",
      legend.box = "vertical",
      legend.margin = ggplot2::margin()
    ) +
    ggplot2::coord_cartesian(
      xlim = c(0, 4)
    )

@@

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```
**Marginal contrasts (exposures: \acr{edcs}; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
Circles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```
**Marginal contrasts (exposures: \acr{edcs}; outcomes: glucocorticosteroids) (HELIX Study; 2013-2016).**
Circles, triangles, and squares indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5)
```
**Marginal contrasts (exposures: glucocorticosteroids; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
Circles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

>>>>

```{r}
# Function to align forest plot with table numerical results
forest_plot <- function(obj, r = 4) {
  edcs <- myphd::edcs_information() |>
    dplyr::filter(!chem_id %in% c("dedtp", "dmdtp")) |>
    dplyr::select(chem_id, short_name, class) |>
    dplyr::bind_rows(
      tibble::tibble(
        chem_id = c("Exposure"),
        short_name = c("Exposure"),
        class = c(NULL)
      )
    )

  # From table of numerical results to ggplot object
  tbl_num_res <- obj$numerical_results |>
    tidylog::mutate(
      variable = forcats::fct_reorder2(
        variable, estimate, class
      )
    ) |>
    tidylog::select(-estimate) |>
    dplyr::left_join(
      edcs[, c("chem_id", "short_name")],
      by = c("variable" = "chem_id")
    ) |>
    dplyr::select(-variable) |>
    dplyr::rename(variable = "short_name") |>
    dplyr::relocate(variable) |>
    ggplot2::ggplot(
      ggplot2::aes(
        y = variable,
        shape = outcome
      )
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 0,
        label = variable
      ),
      hjust = 0,
      fontface = "bold"
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 1,
        label = val
      ),
      hjust = 0,
      position = ggstance::position_dodgev(height = 0.9)
    ) +
    ggplot2::theme_void() +
    ggplot2::theme(
      strip.background = ggplot2::element_blank(),
      strip.text = ggplot2::element_blank(),
      legend.position = "bottom",
      legend.box = "vertical",
      legend.margin = ggplot2::margin()
    ) +
    ggplot2::coord_cartesian(
      xlim = c(0, 4)
    )

@@

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```
**Marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the {{< acr edcs >}} on {{< acr hitrtse >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

@@

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```
**Marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the {{< acr edcs >}} on the glucocorticosteroids expressed in ng/ml (HELIX subcohort; 2013-2016).** 
Circles, triangles, and squares indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

@@

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5)
```
**Marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

### 2024-02-12 output/paper/_si.qmd
Trying to fix Table 1, now with by cohort only in SM. Modifying names EDCs in forest plots.

@@

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    Metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    LLOQ = "loq"
  ) |>
  tidylog::select(-metabolite, Metabolite, LLOQ)
gt::gt(lloq_mets |> dplyr::arrange(Metabolite)) |>
  gt::tab_footnote(
    footnote = "Abbreviations: lower limit of quantification (LLOQ), expressed in nanograms per millilitre."
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Lower limits of quantification for the glucocorticosteroids (HELIX subcohort; 2013-2016).**
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the {{< acr edcs >}} on {{< acr hitrtse >}} (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA |>
    tidylog::filter(
      !grepl("metabolism", outcome)
    ),
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the {{< acr edcs >}} on the glucocorticosteroids (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse >}} (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

>>>>

::: {#supptbl-pop-desc}
```{r pop-desc-full}
targets::tar_load("table1_full", store = store)
table1_full
```
**Participant characteristics, by cohort and overall (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    Metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    LLOQ = "loq"
  ) |>
  tidylog::select(-metabolite, Metabolite, LLOQ)
gt::gt(lloq_mets |> dplyr::arrange(Metabolite)) |>
  gt::tab_footnote(
    footnote = "Abbreviations: lower limit of quantification (LLOQ)."
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Lower limits of quantification expressed in ng/ml for the glucocorticosteroids (HELIX subcohort; 2013-2016).**
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the {{< acr edcs >}} on {{< acr hitrtse >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA |>
    tidylog::filter(
      !grepl("metabolism", outcome)
    ),
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the {{< acr edcs >}} on the glucocorticosteroids expressed in ng/ml (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification by sex of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse >}} expressed in {{< acr mss >}}
 (HELIX subcohort; 2013-2016).** 
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ {{< acr ci >}}.
:::

### 2024-02-12 output/paper/_tables.qmd
Trying to fix Table 1, now with by cohort only in SM. Modifying names EDCs in forest plots.

::: {#tbl-pop-desc}
```{r pop-desc}
targets::tar_load("table1", store = store)
table1
  # gt::cols_width(
  #   label ~ gt::px(300)
  # ) |>
  # gt::tab_style(
  #   style = gt::cell_text(size = gt::pct(90)),
  #   locations = gt::cells_body(
  #     columns = dplyr::everything()
  #   )
  # )
```
**Participant characteristics, by cohort and overall (HELIX subcohort; 2013-2016).**
:::

@@

::: {#tbl-edc-desc}
```{r edc-desc}
targets::tar_load("desc_chems_mets", store = store)
desc_chems_mets$desc_chems
```
**Participants endocrine disruptors concentrations (HELIX subcohort; 2013-2016).**
:::

@@

gtsummary::tbl_merge(
  tbls = list(desc_sums_all, desc_sums_intersection)
) |>
  gtsummary::modify_spanning_header(
    dplyr::everything() ~ NA_character_
  ) |>
  gtsummary::as_gt() |>
  gt::tab_footnote(
    footnote = "Measurements available for the HELIX subcohort.",
    locations = gt::cells_column_labels(8)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Participants derived glucocorticosteroids concentrations, by cohort and overall (HELIX subcohort; 2013-2016).**
:::

@@

dplyr::bind_cols(t1$`_data`, t2$`_data`) |>
  dplyr::select(-`class...4`, -`variable...5`) |>
  dplyr::rename(
    class = "class...1",
    variable = "variable...2"
  ) |>
  dplyr::left_join(
    edcs,
    by = c("variable" = "chem_id")
  ) |>
  dplyr::select(-variable) |>
  dplyr::rename(variable = "short_name") |>
  gt::gt(
    rowname_col = "variable",
    groupname_col = "class"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_footnote(
    footnote = "Estimate and 95% CI.",
    locations = gt::cells_column_labels()
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Pairwise differences between sex-specific marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of {{< acr edcs >}} on {{< acr hitrtse >}} and the glucocorticosteroids (HELIX subcohort; 2013-2016).**
:::

::: {#tbl-hypothesis-3}
```{r hypothesis-3}
tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse >}} (HELIX subcohort; 2013-2016).**
:::

>>>>

::: {#tbl-pop-desc}
```{r pop-desc}
targets::tar_load("table1", store = store)
table1
  # gt::cols_width(
  #   label ~ gt::px(300)
  # ) |>
  # gt::tab_style(
  #   style = gt::cell_text(size = gt::pct(90)),
  #   locations = gt::cells_body(
  #     columns = dplyr::everything()
  #   )
  # )
```
**Participant characteristics (HELIX subcohort; 2013-2016).**
:::

@@

::: {#tbl-edc-desc}
```{r edc-desc}
targets::tar_load("desc_chems_mets", store = store)
desc_chems_mets$desc_chems
```
**Participants endocrine disruptors concentrations expressed in $\mu$grams/L (HELIX subcohort; 2013-2016).**
:::

@@

gtsummary::tbl_merge(
  tbls = list(desc_sums_all, desc_sums_intersection)
) |>
  gtsummary::modify_spanning_header(
    dplyr::everything() ~ NA_character_
  ) |>
  gtsummary::as_gt() |>
  gt::tab_footnote(
    footnote = "Measurements available for the HELIX subcohort.",
    locations = gt::cells_column_labels(8)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Participants derived glucocorticosteroids concentrations expressed in ng/ml, by cohort and overall (HELIX subcohort; 2013-2016).**
:::

@@

dplyr::bind_cols(t1$`_data`, t2$`_data`) |>
  dplyr::select(-`class...4`, -`variable...5`) |>
  dplyr::rename(
    class = "class...1",
    variable = "variable...2"
  ) |>
  dplyr::left_join(
    edcs,
    by = c("variable" = "chem_id")
  ) |>
  dplyr::select(-variable) |>
  dplyr::rename(variable = "short_name") |>
  gt::gt(
    rowname_col = "variable",
    groupname_col = "class"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_footnote(
    footnote = "Estimate and 95% CI.",
    locations = gt::cells_column_labels()
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Pairwise differences between sex-specific marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of {{< acr edcs >}} on {{< acr hitrtse >}}, expressed in {{< acr mss >}}, and the glucocorticosteroids, expressed in ng/ml (HELIX subcohort; 2013-2016).**
:::

::: {#tbl-hypothesis-3}
```{r hypothesis-3}
tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
**Pairwise differences between sex-specific marginal contrasts for the effect of a decrease from the 90th to the 10th percentile of the glucocorticosteroids on {{< acr hitrtse >}} expressed in {{< acr mss >}} (HELIX subcohort; 2013-2016).**
:::
